The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-16 article.tex
Solved https://github.com/richelbilderbeek/raket/issues/4

The PBD model has five biological parameters (see \ref{table:parameters}), 
which we explore in a factorial fashion, excluding some combinations. 
We assume that the speciation initiation and extinction rates
of an incipient and good species are equal ($b_i = b_g$ and $\mu_i = \mu_g$),
as this will result in monophyletic incipient species trees.
We only simulate a PBD process for phylogenies in which
speciation initiation exceeds extinction rate ($b > \mu$),
and in which their difference is not too big ($b - \mu < 0.8$), 
to prevent overly taxon-poor and taxon-rich phylogenies respectively.
The parameter values chosen are a 
superset of \cite{etienne2014}, as these parameters result in reasonably
sized phylogenies and allows us to compare results. 
For the speciation initiation rate $b$, we'll use $0.1$, $0.5$ and $1.0$ 
speciation initiation events per (good species) lineage per time unit.
The speciation completion rates used are $0.1$, $0.3$, $1.0$ and $\infty$ speciation completion
events per (incipient species) lineage per time unit. For $\lambda = \infty$, 
the PBD model equals a BD model, which allows us to measure the baseline error.
The extinction rates used are $0.0$, $0.1$, $0.2$ and $0.4$ 
extinction events per (good or incipient) lineage per time unit.

>>>>

The PBD model has five biological parameters (see \ref{table:parameters}), 
which we explore in a factorial fashion, excluding some combinations. 
We assume that the speciation initiation and extinction rates
of an incipient and good species are equal ($b_i = b_g$ and $\mu_i = \mu_g$),
as this will result in monophyletic incipient species trees.
We only simulate a PBD process for phylogenies in which
speciation initiation exceeds extinction rate ($b > \mu$),
and in which their difference is not too big ($b - \mu < 0.8$), 
to prevent overly taxon-poor and taxon-rich phylogenies respectively.
The parameter values chosen are a 
superset of \cite{etienne2014}, as these parameters result in reasonably
sized phylogenies and allows us to compare results. 
For the speciation initiation rate $b$, we'll use $0.1$, $0.5$ and $1.0$ 
speciation initiation events per (good species) lineage per time unit.
The speciation completion rates used are $0.1$, $0.3$, $1.0$ and $10^9$ speciation completion
events per (incipient species) lineage per time unit. For 
$\lambda = \infty$ (where we assume that in this context $10^9 \approx \infty$), 
the PBD model equals a BD model, which allows us to measure the baseline error.
The extinction rates used are $0.0$, $0.1$, $0.2$ and $0.4$ 
extinction events per (good or incipient) lineage per time unit.
